---
title: "RWorksheet_Elizalde#1"
author: "Christian Alimace Elizalde"
date: "2024-09-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1. Set up a vector named age, consisting of 34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,51, 35, 24, 33, 41.

```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```
#a. How many data points?
```{r}
length(age)
```
#b. Write the R code and its output. 

#Find the reciprocal values for age.
```{r}
library("MASS")
reciprocalOfage <- 1/age
fractions(reciprocalOfage)
```

#Assign also new_age <- c(age, 0, age)
```{r}
new_age <- c(age, 0, age)
new_age
```

#sort the values for age
```{r}
sort(age)
```

#Find the minimum and maximum value for age
```{r}
min(age)
max(age)
```

#Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, and 2.7.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
```

#How many data points?
```{r}
length(data)
```

#Generates a new vector for data where you double every value of the data. 
```{r}
doubled_data <- 2 * (data)
doubled_data
```

#Generate a sequence for the following scenario:8.1 Integers from 1 to 100.
```{r}
sequence_1to100 <- seq(1:100)
```

#8.2 Numbers from 20 to 60
```{r}
sequence_20to60 <- (20:60)
```

#8.3 Mean from 20 to 60
```{r}
mean_sequence <- mean(sequence_20to60)
mean_sequence
```

#8.4 Sum of numbers from 51 to 91
```{r}
summation <- sum(51:91)
summation
```

#8.5 Integers from 1 to 1,000
```{r}
sequence_1to1000 <- seq(1:1000)
```

#a. how many data points from 8.1 to 8.4?
```{r}
length(sequence_1to100) + length(sequence_20to60) + length(mean_sequence) + length(summation)
```

#9. *Print a vector with the integers between 1 and 100 that are not divisible by 3, 5 and 7 using filter option.
```{r}
Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))
```

#10 Generate a sequence backwards of the integers from 1 to 100.
```{r}
backwards <- seq(100:1)
backwards
```

#11. List all the natural numbers below 25 that are multiples of 3 or 5. Find the sum of these multiples.
```{r}
below_25 <- seq(1:24)
multiplesof3or5 <- below_25[below_25 %% 3 == 0 | below_25 %% 5 == 0] 
multiplesof3or5
sum(multiplesof3or5)
```

#a. How many data points from 10 to 11?
```{r}
length(backwards) + length(multiplesof3or5)
```

#12
```{r}
#x <- {0 + x + 5 + } this code produces error
```

#13 *Set up a vector named score, consisting of 72, 86, 92, 63, 88, 89, 91, 92, 75, 75 and 77. To access individual elements of an atomic vector, one generally uses the x[i] construction.
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
score[2]
score[3]
```

#*Create a vector a = c(1,2,NA,4,NA,6,7).
```{r}
a = c(1,2,NA,4,NA,6,7)
```

#a. Change the NA to 999 using the codes print(a,na.print="-999").
```{r}
print(a,na.print="-999")
```

#15. A special type of function calls can appear on the left hand side of the assignment operator as in > class(x) <- "foo".
```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age,"years old."))
print(R.version.string)
```





