---
title: "RWorksheet_Elizalde#4a"
author: "Christian Alimace Elizalde"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
new_data <- read.csv("/cloud/project/Rworksheet4a/SshG.csv")
new_data
```
#a. Describe the data.
#the data shows the shoe size, height, and gender.

#b. Create a subset by males and females with their corresponding shoe size and height. What its result? Show the R scripts.
```{r}
male <- subset(new_data, Gender == "M" & Height & Shoe.size)
male
female <- subset(new_data, Gender == "F" & Height & Shoe.size)
female

```
#c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
mSS <- mean(new_data$Shoe.size)
mSS
mH <- mean(new_data$Height)
mH
```
#d. Is there a relationship between shoe size and height? Why?
#Yes because taller individuals have larger shoe size while small individuals have smaller shoe size.

#2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August","July","December","August","August","September","November","February","April")
months
```
```{r}
factor_months_vector <- factor(months)
factor_months_vector
```

#3. Then check the summary() of the months_vector and factor_months_vector. | Inter-pret the results of both vectors. Are they both equally useful in this case?
#The result of months vector prints the length, class, and mode while the factor_months_vector prints the number of how many times a month has been mentioned in the vector. They are both useful.
```{r}
summ <- summary(months)
summ
```
```{r}
fsumm <- summary(factor_months_vector)
fsumm
```
#4. Create a vector and factor for the table below.
```{r}
Direction <- c("East", "West", "North")
Frequency <- c(1,4,3)
factor_data <- data.frame(Direction, Frequency)
factor_data
```
```{r}
new_order_data <- factor(factor_data, levels = c("East","West","North"))
print(new_order_data)
```
#5. Enter the data below in Excel with file name = import_march.csv
#a. Import the excel file into the Environment Pane using read.table() function. Write the code.
```{r}
readT <- read.table("import_march.csv", header = TRUE, sep = ",")
readT
```
#b. View the dataset. Write the R scripts and its result.
```{r}
print(readT)
```
#6. Full Search

```{r}
num <- as.numeric(readline(prompt = "Enter a number from 1 to 50: "))
if(!is.na(num) == 20){
  print("TRUE")
}else if (!is.na(num) >=1 && num <=50){
  num
}else {
  print("The number selected is beyond the range of 1 to 50.")
}

```
#7. Change
```{r}
snack <- as.numeric(readline(prompt="Enter price of snack: "))
minBills <- function(snack) {
  bills <- 0
  
  if (!is.na(snack) >= 1000) {
    bills <- bills + snack %/% 1000
    snack <- snack %% 1000
  }
  if (!is.na(snack) >= 500) {
    bills <- bills + snack %/% 500
    snack <- snack %% 500
  }
  if (!is.na(snack) >= 200) {
    bills <- bills + snack %/% 200
    snack <- snack %% 200
  }
  if (!is.na(snack) >= 100) {
    bills <- bills + snack %/% 100
    snack <- snack %% 100
  }
  if (!is.na(snack) >= 50) {
    bills <- bills + snack %/% 50
    snack <- snack %% 50
  }
  return(bills)
}
minBills(snack)


```
#8. 
#a. create a data frame frome the above table. Write the codes and its output
```{r}
df <- data.frame(Name = c("Annie", "Thea", "Steve", "Hanna"),
                 Grade1 = c(85, 65, 75, 95),
                 Grade2 = c(65, 75, 55, 75),
                 Grade3 = c(85, 90, 80, 100),
                 Grade4 = c(100, 90, 85, 90))
df
```
#b. 
```{r}
avg_scores <- rowSums(df[,-1]) / (ncol(df) - 1)
if (any(avg_scores > 90)) {
high_avg_names <- df$Name[avg_scores > 90]
high_avg_scores <- avg_scores[avg_scores > 90]
print0(paste(high_avg_names, "'s average grade this semester is ", high_avg_scores))
} else {
cat("No student's average grade is over 90.")
}


```

#c.
```{r}
test_avg <- colSums(df[, -1]) / nrow(df)

if(any(test_avg < 80)){
  test_hard <- which(test_avg<80)

cat(paste("The test", test_hard, "was difficult."))
 }else {
cat("All tests had an average scores of 80 or above.")

}
```
#d.
```{r}
high_score <- apply(df[,-1], 1, function(x) sort(x, decreasing = TRUE)[1])
if (any(high_score > 90)) {
hnames <- df$Name[high_score > 90]
hscores <- high_score[high_score > 90]
cat(paste(hnames, "'s highest grade this semester is ", hscores,".\n"))
} else {
cat("No student's highest grade exceeded 90.")
}

```

