---
title: "RWorksheet_Elizalde#4b"
author: "Christian Alimace Elizalde"
date: "2024-10-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. 
```{r}
vectorA <- c(1, 2, 3, 4, 5)

result <- matrix(0, nrow = 5, ncol = 5)

for (i in 1:5) {
  for (j in 1:5) {
   result[i, j] <- abs(vectorA[i] - vectorA[j])
  }
}
print(result)

```
#2.
```{r}
l <- 5

for (i in 1:l){
  for (p in 1:i){
    cat("*")
  }
  cat("\n")
  }

```
#3.
```{r}
input <- as.integer(readline(prompt = "Enter the starting number for Fibonacci Sequence: "))

a <- 0
b <- 1

repeat{
  nextnum <- a+b
  
  if(!is.na(nextnum) > 500){ break
  }
  a <- b
  b <- nextnum
  
  if(!is.na(nextnum) >= input){
    cat(nextnum, "\n")
  }
}
```
#4. 
#a.
```{r}
df1 <- read.csv("/cloud/project/Rworksheet4b/HouseholdData.csv")
df1

head(df1, 6)
```
#b. Both has 14 observations
```{r}
m <- subset(df1, Sex == "Male")
m
f <- subset(df1, Sex == "Female")
f
males <- nrow(m)
females <- nrow(f)
cat("Number of observations for Male:", males, "\n")
cat("Number of observations for Female:", females, "\n")
```
#c.
```{r}
bplot <- c(males,females)
names(bplot) <- c("Male", "Female")
barplot(bplot, main = "Male and Female", xlab = "Gender", ylab = "Total Numbers", col = c("blue", "pink"),legend.text = TRUE, beside = TRUE)

```
#5. 
```{r}
bills <- c("Food", "Electricity", "Savings", "Miscellaneous")
values <- c(60, 10, 5, 25)


Plotters <- pie(values, labels = c("Food", "Electricity", "Savings", "Miscellaneous"),col = c("lightblue", "yellow", "orange", "red"), main = "Expenditures" )
```
#6.
#a.
```{r}
data(iris)
str(iris)
```
#b.
```{r}
meanI <- colMeans(iris[, 1:4])
meanI
```
#c
```{r}
speciesC <- table(iris$Species)
pie(speciesC, main="Species Distribution", col=c("pink", "yellow", "purple"), labels=names(speciesC))
```
#d
```{r}
setosa <- subset(iris, Species == "setosa")
versicolor <- subset(iris, Species == "versicolor")
virginica <- subset(iris, Species == "virginica")
tail(setosa, 6)
tail(versicolor, 6)
tail(virginica, 6)
```
#e
```{r}
plot(iris$Sepal.Length, iris$Sepal.Width, col=iris$Species, pch=19,
main="Iris Dataset", xlab="Sepal Length", ylab="Sepal Width",
sub="Sepal Width vs Length by Species")
legend("topright", legend=levels(iris$Species), col=1:3, pch=19)
```
#f. Based on Sepal Length and Sepal Width, the scatterplot clearly differentiates Setosa from the other two species. The sepals of Setosa form a unique cluster and are notably wider and shorter. Although virginica often has longer sepals, versicolor and virginica overlap more, especially in sepal width. Longer sepals are often narrower, with a little negative association, particularly in virginica.
#7. #a.
```{r}
library("openxlsx")
library("readxl")
alexa <- read_excel("/cloud/project/Rworksheet4b/alexa_file.xlsx")

alexa$variation <- gsub("Black  Dot", "BlackDot", alexa$variation)
alexa$variation <- gsub("Black  Plus", "BlackPlus", alexa$variation)
alexa$variation <- gsub("Black  Show", "BlackShow", alexa$variation)
alexa$variation <- gsub("Black  Spot", "BlackSpot", alexa$variation)
alexa$variation <- gsub("White  Dot", "WhiteDot", alexa$variation)
alexa$variation <- gsub("White  Plus", "WhitePlus", alexa$variation)
alexa$variation <- gsub("White  Show", "WhiteShow", alexa$variation)
alexa$variation <- gsub("White  Spot", "WhiteSpot", alexa$variation)

knitr::include_graphics("/cloud/project/Rworksheet4b/SS.jfif")

```
#b
```{r}
library(dplyr)

variations.RData <- alexa %>%
  count (alexa$variation)

save(variations.RData, file = "variations.RData")
print(variations.RData)

```
#c. 
```{r}
barplot(
  variations.RData$n,  
  names.arg = variations.RData$`alexa$variation`,  
  cex.names = 0.4,  
  main = "Count of Variations",
  ylab = "Count",
  col = rainbow(length(variations.RData$n)),  
  border = "black",  
  las = 2  
)

```
#d. 
```{r}
samps <- brewer.pal(5, "Dark2")

blacks <- variations.RData %>%
  filter(grepl("^Black|^White", `alexa$variation`))
par(mfrow = c(1, 2))
barplot(
  blacks$n[blacks$`alexa$variation` %in% c("Black", "BlackPlus", "BlackShow", "BlackSpot", "BlackDot")], 
  names.arg = blacks$`alexa$variation`[blacks$`alexa$variation` %in% c("Black", "BlackPlus", "BlackShow", "BlackSpot", "BlackDot")], 
  las = 3,
  cex.names = 1,
  main = "Black Variations",         
  ylab = "Count",                             
  col = samps,
  border = "black"
)
barplot(
  blacks$n[blacks$`alexa$variation` %in% c("White", "WhitePlus", "WhiteShow", "WhiteSpot", "WhiteDot")], 
  names.arg = blacks$`alexa$variation`[blacks$`alexa$variation` %in% c("White", "WhitePlus", "WhiteShow", "WhiteSpot", "WhiteDot")], 
  las = 2,
  cex.names = 1,
  main = "White Variations",         
  ylab = "Count",                              
  col = c("blue", "green", "yellow", "purple", "pink"),                              
  border = "black"                           
)
```

